### 2024-04-30 thesis/sections/7-language-analysis.tex
language analysis

\section{Analysis of the emerged languages}
\label{sec:analysis_language}
The languages that emerge are analyzed in two ways.
An analysis of the frequency of used symbols and messages, as well as an examination for which images and objects they are used indicates the structure of the language and meanings of the symbols.
In a second step, the language is compared to several referring expressions in natural language.
By doing this, it can be seen if the models learned to use similar ways of referring to objects as humans do, or if they rely on different approaches.
% from prev chapter

To compare the emerged language to English in a \textbf{quantitative} way, a probing approach is used.
Probing can be used to analyze and interpret the hidden representations in neural networks.
Hereby, a second neural model is trained to predict selected linguistic properties on the basis of the hidden representations.
If this model is successfully able to predict the linguistic properties, the hidden representations are connected to them.
If second model can't be trained, it indicates that there is no correlation between the hidden representation and the linguistic property.
In the case of the emerged language, a neural model is trained to translate the messages of the sender into English referring expressions, based on the GRE algorithm by \citet{Dale1995}.
% SD: The probing test is to show how well the emerged language can be trasnlated into English descriptions consistting of labels of scene features using Dale and Reiter idea of incrementality. However, we would need to know now what was the policy of the sender to generate message. Was this similar to Dale and Reiter to enforce longer descriptions?
% DK: TODO
Hereby, the model consists of an encoder LSTM, one linear layer and a decoder LSTM.
The encoder LSTM encodes the messages of the emerged language.
The final hidden state is used as the meaning of the complete sentence and passed through the linear layer, which should learn an abstract representation of the message.
The resulting vector is used as the initial state of the decoder LSTM.
The decoder LSTM is then trained to produce the English referring expression.
While decoding, teacher forcing is applied.
The success of the model is validated calculating cross entropy between the models predictions and the target English referring expression.
Since generalization doesn't play a role for probing, no dropout is applied and the model is trained and validated on the complete dataset; no test or validation split is used.

In the sections above, the attributes are ordered by importance in the way, it is usually used in English: shape > color > size.
Since the agents do not necessarily need to follow this, all possible orders of importance for the attributes are compared to each other.
% SD: Move to the earlier paragraph when you introduce Dale and Reiter.
% DK: TODO

The translation model with this setup can learn two characteristics.
First, it can learn to find correlations between the emerged language and the English referring expressions.
Secondly, it can learn patterns in the English referring expressions that are independent of the emerged language.
For instance, it can learn that the referring expressions are likely to be two symbols long, or that 'cube' is the most common shape.
This second characteristic can lead to a low loss of the model, even though there are no connections to the emerged language.
In this test, only the first characteristic is interesting and would show the correlation between the emerged language and English referring expressions.
For that reason, two reference baselines are calculated for each of the attribute importance order.
% SD: Baselines?
% DK: (done)
The first reference uses a non-informative input for the encoder LSTM, more specifically it always receives a vector of zeros and therefore can't learn any meaningful representation in the linear layer; the input for the decoder LSTM is the same for every sample.
By this, the model is trained to learn the patterns in the English referring expressions.
The resulting loss is the highest possible loss the model can achieve, independent of the input.
Resulting, if the emergent language is connected to English, the loss will be lower than this baseline.
If not, the loss will be as high as this baseline.
On the other side, we calculated the lowest loss possible, by using the English referring expressions as both input and target.
This verifies that the model is able to learn an abstract representation from the input and the resulting loss should be close to zero (since input is perfectly correlated to the target).
These two references are used, to normalize the results of the actual emergent languages $L_{em}$, using the formula $L_{norm} = \frac{L_{em}-L_{English}}{L_{baseline} - L_{English}}$.
A loss close as $L_{baseline}$ will lead to 100\%, while a loss as $L_{English}$ will lead to 0\%.
% SD: Is this encessary? But when and where is this loss using 0 inouts calculated?
% DK: TODO, QUESTION
By doing this, all configurations can be compared directly to each other.

@@

    \label{TODO: label}

@@

    \label{TODO: label}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C}     & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {1} & {2}   & \textcolor{red}{91,62\%} & \textcolor{red}{91,57\%} & \textcolor{red}{94,31\%} & \textcolor{red}{95,13\%} & \textcolor{red}{93,11\%} & \textcolor{red}{94,92\%} \\
        {1} & {10}  & {79,08\%}                & {79,08\%}                & {85,04\%}                & {86,86\%}                & {82,37\%}                & {86,38\%}                \\
        {1} & {16}  & {84,02\%}                & {83,96\%}                & {88,67\%}                & {89,65\%}                & {86,36\%}                & {89,36\%}                \\
        {1} & {50}  & \textcolor{red}{93,88\%} & \textcolor{red}{93,74\%} & \textcolor{red}{95,03\%} & \textcolor{red}{95,49\%} & \textcolor{red}{94,64\%} & \textcolor{red}{95,35\%} \\
        {2} & {10}  & {88,67\%}                & {88,36\%}                & {89,59\%}                & \textcolor{red}{90,77\%} & \textcolor{red}{90,01\%} & {89,81\%}                \\
        {2} & {16}  & {81,13\%}                & {81,02\%}                & {86,16\%}                & {87,97\%}                & {83,85\%}                & {87,56\%}                \\
        {3} & {2}   & {83,38\%}                & {83,46\%}                & {88,21\%}                & {89,71\%}                & {86,05\%}                & {89,37\%}                \\
        {3} & {10}  & \textbf{77\%}            & \textbf{76,77\%}         & \textbf{83,54\%}         & \textbf{85,57\%}         & \textbf{79,97\%}         & \textbf{84,9\%}          \\
        {3} & {16}  & \textcolor{red}{93,52\%} & \textcolor{red}{93,6\%}  & \textcolor{red}{94,16\%} & \textcolor{red}{94,14\%} & \textcolor{red}{93,75\%} & \textcolor{red}{93,55\%} \\
        {4} & {10}  & \textbf{68,04\%}         & \textbf{66,51\%}         & \textbf{76,33\%}         & \textbf{78,56\%}         & \textbf{71,42\%}         & \textbf{78,56\%}         \\
        {4} & {16}  & \textbf{75,1\%}          & \textbf{74,93\%}         & \textbf{81,2\%}          & \textbf{83,35\%}         & \textbf{77,6\%}          & \textbf{82,76\%}         \\
        {6} & {2}   & {84,21\%}                & {84,02\%}                & {88,41\%}                & {89,77\%}                & {86,61\%}                & {89,35\%}                \\
        \bottomrule
    \end{tabular}
    \caption{Discriminator: Color}
    \label{TODO: label}
\end{table}

@@

    \label{TODO: label}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}              & \textbf{C > Si > Sh} & \textbf{Sh > C > Si}              & \textbf{Sh > Si > C} & \textbf{Si > C > Sh} & \textbf{Si > Sh > C} \\\midrule
        {1} & {2}   & \textcolor{red}{95,35\%}          & {89,87\%}            & \textcolor{red}{95,09\%}          & {87,23\%}            & {86,01\%}            & {84,14\%}            \\
        {1} & {16}  & \textcolor{red}{92,95\%}          & {87,03\%}            & \textcolor{red}{92,63\%}          & {83,91\%}            & {82,77\%}            & {80,06\%}            \\
        {1} & {50}  & \textcolor{red}{93,35\%}          & {87,23\%}            & \textcolor{red}{93,26\%}          & {84,65\%}            & {82,46\%}            & {80,38\%}            \\
        {2} & {10}  & \textbf{88,94\%}                  & \textbf{84,78\%}     & \textbf{87,5\%}                   & \textbf{77,76\%}     & \textbf{80,24\%}     & \textbf{74,95\%}     \\
        {2} & {16}  & \textbf{85,71\%}                  & \textbf{84,53\%}     & \textbf{82,98\%}                  & \textbf{72,85\%}     & \textbf{79,72\%}     & \textbf{71,85\%}     \\
        {3} & {16}  & \textcolor{red}{\textbf{92,18\%}} & \textbf{86,23\%}     & \textcolor{red}{91,93\%}          & \textbf{82,59\%}     & \textbf{81,69\%}     & \textbf{78,72\%}     \\
        {3} & {50}  & \textcolor{red}{92,68\%}          & {86,53\%}            & \textcolor{red}{91,9\%}           & {83,35\%}            & {82,45\%}            & {79,99\%}            \\
        {6} & {10}  & \textcolor{red}{93,4\%}           & {86,51\%}            & \textcolor{red}{\textbf{91,64\%}} & {84,03\%}            & {82,51\%}            & {80,06\%}            \\
        \bottomrule
    \end{tabular}
    \caption{Attention predictor: Dale-5}
    \label{TODO: label}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C}     & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {3} & {16}  & \textcolor{red}{98,48\%} & \textcolor{red}{98,58\%} & \textcolor{red}{97,87\%} & \textcolor{red}{96,11\%} & \textcolor{red}{96,6\%}  & \textcolor{red}{95,97\%} \\
        {4} & {10}  & \textcolor{red}{98,88\%} & \textcolor{red}{98,75\%} & \textcolor{red}{97,23\%} & \textcolor{red}{96,67\%} & \textcolor{red}{97,18\%} & \textcolor{red}{96,75\%} \\
        \bottomrule
    \end{tabular}
    \caption{Attention predictor: Color}
    \label{TODO: label}
\end{table}

@@

    \label{TODO: label}

@@

    \label{TODO: label}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si} & \textbf{Sh > Si > C} & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C} \\\midrule
        {1} & {2}   & \textcolor{red}{99,92\%} & \textcolor{red}{99,88\%} & \textbf{79,83\%}     & \textbf{82,7\%}      & \textcolor{red}{99,71\%} & \textbf{82,14\%}     \\
        {1} & {10}  & \textbf{70,52\%}         & \textbf{70,36\%}         & \textbf{80,23\%}     & \textbf{82,36\%}     & \textbf{74,49\%}         & \textbf{81,77\%}     \\
        {1} & {16}  & \textbf{77,25\%}         & \textbf{77,16\%}         & {84,55\%}            & {86,2\%}             & \textbf{80,72\%}         & {85,56\%}            \\
        {3} & {10}  & \textbf{71,46\%}         & \textbf{71,47\%}         & \textbf{78,81\%}     & \textbf{81,87\%}     & \textbf{75,95\%}         & \textbf{80,93\%}     \\
        {6} & {2}   & {83,25\%}                & {83,23\%}                & {87,74\%}            & {88,95\%}            & {85,38\%}                & {88,87\%}            \\
        \bottomrule
    \end{tabular}
    \caption{Attribute generator: Color}
    \label{TODO: label}
\end{table}

@@

    \label{TODO: label}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C} & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {1} & {2}   & \textcolor{red}{92,86\%} & \textcolor{red}{96,4\%}  & \textcolor{red}{90,06\%} & {89,5\%}             & \textcolor{red}{95,73\%} & \textcolor{red}{90,93\%} \\
        {1} & {10}  & {83,9\%}                 & \textcolor{red}{90,9\%}  & {78,63\%}                & {74,74\%}            & {89,6\%}                 & {78,99\%}                \\
        {1} & {16}  & {84,68\%}                & \textcolor{red}{91,65\%} & {80,11\%}                & {77,03\%}            & \textcolor{red}{90,16\%} & {81,05\%}                \\
        {1} & {50}  & {84,85\%}                & \textcolor{red}{91,67\%} & {79,95\%}                & {77,11\%}            & \textcolor{red}{90,32\%} & {81,04\%}                \\
        {2} & {2}   & \textcolor{red}{90,51\%} & \textcolor{red}{95,36\%} & {87,5\%}                 & {86,43\%}            & \textcolor{red}{94,77\%} & {88,35\%}                \\
        {2} & {10}  & {82,44\%}                & \textcolor{red}{90,32\%} & {77,65\%}                & {73,73\%}            & {88,89\%}                & {78,41\%}                \\
        {2} & {16}  & {81,85\%}                & \textbf{89,4\%}          & {76,07\%}                & \textbf{71,66\%}     & {87,9\%}                 & \textbf{75,91\%}         \\
        {2} & {50}  & {83,58\%}                & \textcolor{red}{91,12\%} & {78,67\%}                & {75,03\%}            & {89,94\%}                & {79,06\%}                \\
        {3} & {2}   & \textcolor{red}{92,51\%} & \textcolor{red}{95,96\%} & {89,96\%}                & {88,7\%}             & \textcolor{red}{95,18\%} & \textcolor{red}{90,43\%} \\
        {3} & {10}  & {82,11\%}                & {89,54\%}                & {75,9\%}                 & {71,78\%}            & {88,18\%}                & {76,72\%}                \\
        {3} & {50}  & {83,12\%}                & \textcolor{red}{90,82\%} & {77,62\%}                & {74,08\%}            & {88,88\%}                & {78,74\%}                \\
        {3} & {100} & {83,74\%}                & {89,59\%}                & {79,29\%}                & {74,48\%}            & \textbf{87,46\%}         & {78,05\%}                \\
        {4} & {2}   & {88,86\%}                & \textcolor{red}{94\%}    & {84,8\%}                 & {83,19\%}            & \textcolor{red}{93,37\%} & {85,92\%}                \\
        {4} & {10}  & \textbf{79,93\%}         & \textbf{89,29\%}         & \textbf{74,1\%}          & \textbf{69,5\%}      & \textbf{87,19\%}         & \textbf{74,79\%}         \\
        {4} & {16}  & \textbf{81,26\%}         & {89,68\%}                & \textbf{75,73\%}         & {71,96\%}            & {88,4\%}                 & {76,93\%}                \\
        {4} & {50}  & {81,55\%}                & {89,42\%}                & {75,9\%}                 & {71,68\%}            & {88,17\%}                & {76,55\%}                \\
        {6} & {2}   & \textcolor{red}{91,09\%} & \textcolor{red}{95,26\%} & {87,86\%}                & {86,81\%}            & \textcolor{red}{94,78\%} & {88,82\%}                \\
        {6} & {50}  & \textbf{80,39\%}         & \textbf{87,85\%}         & \textbf{75,01\%}         & \textbf{68,71\%}     & \textbf{84,54\%}         & \textbf{72,93\%}         \\
        \bottomrule
    \end{tabular}
    \caption{RE generator: Dale-5}
    \label{TODO: label}
\end{table}

>>>>

\section{Analysis of the emerged languages}
\label{sec:analysis_language}
The languages that emerge are analyzed in two ways.
First, for each language that emerges through successful communication, a score is calculated that represents the similarity of the messages to valid English referring expressions.
In a second step, several languages are analyzed qualitatively, to determine what certain symbols mean and what they might refer to in the visual scenes.
\cmtDK[inline]{talks about why and which few languages}

To compare the emerged language to English in a \textbf{quantitative} way, a probing approach is used.
Probing can be used to analyze and interpret the hidden representations in neural networks.
Hereby, a second neural model is trained to predict selected linguistic properties on the basis of the hidden representations.
If this model is successfully able to predict the linguistic properties, the hidden representations are connected to them.
If second model can't be trained, it indicates that there is no correlation between the hidden representation and the linguistic property.
In the case of the emerged language, a neural model is trained to translate the messages of the sender into English referring expressions, based on the GRE algorithm by \citet{Dale1995}.
Recall, that this incremental is based on an order in salience for the attributes.
In English, \citet{Dale1995} propose the order of \emph{shape} > \emph{color} > \emph{size}.
However, there is no policy for the agents, that enforces specifically this order or indeed any salience order.
For this reason, the emerged languages are compared to all possible salience orders, given the three attributes \emph{shape}, \emph{color} and \emph{size}.
This will show if first, the languages follow any salience order and secondly, which attributes are more important for the agents to communicate.
% SD: The probing test is to show how well the emerged language can be trasnlated into English descriptions consistting of labels of scene features using Dale and Reiter idea of incrementality. However, we would need to know now what was the policy of the sender to generate message. Was this similar to Dale and Reiter to enforce longer descriptions?
% DK: done

The probing model consists of an encoder LSTM, one linear layer and a decoder LSTM.
The encoder LSTM encodes the messages of the emerged language.
Its final hidden state is used as a representation of the meaning of the complete message and passed through the linear layer, which learns an abstract representation of the message.
The dimension of the linear layer is kept small to prevent memorizing the dataset and force the model to find abstract connections between the input and the target.
The resulting vector is used as the initial state of the decoder LSTM.
The decoder LSTM is then trained to produce the English referring expression.
Both LSTMs have an embedding dimension of $LSTM_e=10$ and a hidden size of $LSTM_{out}=10$, while the linear layer has a size of $l=10$.
During decoding, teacher forcing is applied.
The success of the model is validated calculating cross entropy between the models predictions and the target English referring expression.
Since generalization doesn't play a role for probing, no dropout is applied and the model is trained and validated on the complete dataset; no test or validation split is used.
The models are trained for 200 epochs with a learning rate of $lr=0,004$ and a batch size of 32 samples per batch.

The translation model will learn two characteristics with this setup.
First, it can learn to find correlations between the emerged language and the English referring expressions, which is the goal of the probing.
But secondly, it can also learn underlying patterns in the English referring expressions that are independent of the emerged language.
For instance, it can learn that the referring expressions are likely to be two symbols long, or that for instance 'cube' is the most common shape.
This second characteristic will lead to a low loss during training, even though there are no connections to the emerged language.
In this test, only the first characteristic is interesting and would show the correlation between the emerged language and English referring expressions.
For that reason, two reference baselines are calculated for each salience order of the attributes, to eliminate the influence of the second characteristic.
% SD: Baselines?
% DK: (done)
The first baseline $L_{baseline}$ uses a non-informative input for the encoder LSTM, more specifically it always receives a vector of zeros and therefore can't learn any meaningful representation in the linear layer; the input for the decoder LSTM is the same for every sample.
By this, the model is trained to learn the structural patterns in the English referring expressions.
The resulting loss is the highest possible loss the model can achieve, independent of the input.
Resulting, if the emergent language is connected to English, the loss will be lower than this baseline.
If not, the loss will be as high as this baseline.
On the other side, the lowest possible loss $L_{English}$ is calculated, by using the English referring expressions as both input and target.
This verifies that the model is able to learn an abstract representation from the input and the resulting loss should be close to zero (since the input is perfectly correlated to the target).
These two references are used, to normalize the results of the actual emergent languages $L_{em}$, using the formula $L_{norm} = \frac{L_{em}-L_{English}}{L_{baseline} - L_{English}}$.
A loss close to $L_{baseline}$ will lead to 100\%, while a loss as $L_{English}$ will lead to 0\%.
% SD: Is this encessary? But when and where is this loss using 0 inouts calculated?
% DK: TODO, QUESTION
By doing this, all configurations can be compared directly to each other.
The lower $L_{norm}$, the higher the correlation between the emerged language and English referring expressions.

Tables \ref{tab:probing:discriminator:dale-2} to \ref{tab:probing:attention-predictor:colour} show the normalized losses $L_{norm}$ of the probing for the different tasks on all three datasets.
Hereby, only languages are listed for experiments in which the agents communicated successfully, that is $L_{norm}$ is lower than 100\%.
The first thing that can be noticed is that across almost all languages emerged through successful communication, $L_{norm}$ is lower than 100\% with at least one salience order, which shows that they make use of the attributes in some way.
On the other side, no language reaches an $L_{norm}$ close to 0, that is no language correlates perfectly with English referring expressions.
The closest is a language with $L_{norm}$ just above 40\%.
This shows that while many emerged languages have similarities with English, they make use of either other additional visual characteristics in the scenes or use different linguistic structures.

@@

    \label{tab:probing:discriminator:dale-2}

@@

    \label{tab:probing:discriminator:dale-5}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C}     & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {1} & {2}   & \textcolor{red}{91,62\%} & \textcolor{red}{91,57\%} & \textcolor{red}{94,31\%} & \textcolor{red}{95,13\%} & \textcolor{red}{93,11\%} & \textcolor{red}{94,92\%} \\
        {1} & {10}  & {79,08\%}                & {79,08\%}                & {85,04\%}                & {86,86\%}                & {82,37\%}                & {86,38\%}                \\
        {1} & {16}  & {84,02\%}                & {83,96\%}                & {88,67\%}                & {89,65\%}                & {86,36\%}                & {89,36\%}                \\
        {1} & {50}  & \textcolor{red}{93,88\%} & \textcolor{red}{93,74\%} & \textcolor{red}{95,03\%} & \textcolor{red}{95,49\%} & \textcolor{red}{94,64\%} & \textcolor{red}{95,35\%} \\
        {2} & {10}  & {88,67\%}                & {88,36\%}                & {89,59\%}                & \textcolor{red}{90,77\%} & \textcolor{red}{90,01\%} & {89,81\%}                \\
        {2} & {16}  & {81,13\%}                & {81,02\%}                & {86,16\%}                & {87,97\%}                & {83,85\%}                & {87,56\%}                \\
        {3} & {2}   & {83,38\%}                & {83,46\%}                & {88,21\%}                & {89,71\%}                & {86,05\%}                & {89,37\%}                \\
        {3} & {10}  & \textbf{77\%}            & \textbf{76,77\%}         & \textbf{83,54\%}         & \textbf{85,57\%}         & \textbf{79,97\%}         & \textbf{84,9\%}          \\
        {3} & {16}  & \textcolor{red}{93,52\%} & \textcolor{red}{93,6\%}  & \textcolor{red}{94,16\%} & \textcolor{red}{94,14\%} & \textcolor{red}{93,75\%} & \textcolor{red}{93,55\%} \\
        {4} & {10}  & \textbf{68,04\%}         & \textbf{66,51\%}         & \textbf{76,33\%}         & \textbf{78,56\%}         & \textbf{71,42\%}         & \textbf{78,56\%}         \\
        {4} & {16}  & \textbf{75,1\%}          & \textbf{74,93\%}         & \textbf{81,2\%}          & \textbf{83,35\%}         & \textbf{77,6\%}          & \textbf{82,76\%}         \\
        {6} & {2}   & {84,21\%}                & {84,02\%}                & {88,41\%}                & {89,77\%}                & {86,61\%}                & {89,35\%}                \\
        \bottomrule
    \end{tabular}
    \caption{Discriminator: Color}
    \label{tab:probing:discriminator:colour}
\end{table}

Looking at the results for the discriminator, one can see that the results are very different for each dataset.
On the 'Dale-2' dataset

@@

    \label{tab:probing:re-generator:dale-2}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C} & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {1} & {2}   & \textcolor{red}{92,86\%} & \textcolor{red}{96,4\%}  & \textcolor{red}{90,06\%} & {89,5\%}             & \textcolor{red}{95,73\%} & \textcolor{red}{90,93\%} \\
        {1} & {10}  & {83,9\%}                 & \textcolor{red}{90,9\%}  & {78,63\%}                & {74,74\%}            & {89,6\%}                 & {78,99\%}                \\
        {1} & {16}  & {84,68\%}                & \textcolor{red}{91,65\%} & {80,11\%}                & {77,03\%}            & \textcolor{red}{90,16\%} & {81,05\%}                \\
        {1} & {50}  & {84,85\%}                & \textcolor{red}{91,67\%} & {79,95\%}                & {77,11\%}            & \textcolor{red}{90,32\%} & {81,04\%}                \\
        {2} & {2}   & \textcolor{red}{90,51\%} & \textcolor{red}{95,36\%} & {87,5\%}                 & {86,43\%}            & \textcolor{red}{94,77\%} & {88,35\%}                \\
        {2} & {10}  & {82,44\%}                & \textcolor{red}{90,32\%} & {77,65\%}                & {73,73\%}            & {88,89\%}                & {78,41\%}                \\
        {2} & {16}  & {81,85\%}                & \textbf{89,4\%}          & {76,07\%}                & \textbf{71,66\%}     & {87,9\%}                 & \textbf{75,91\%}         \\
        {2} & {50}  & {83,58\%}                & \textcolor{red}{91,12\%} & {78,67\%}                & {75,03\%}            & {89,94\%}                & {79,06\%}                \\
        {3} & {2}   & \textcolor{red}{92,51\%} & \textcolor{red}{95,96\%} & {89,96\%}                & {88,7\%}             & \textcolor{red}{95,18\%} & \textcolor{red}{90,43\%} \\
        {3} & {10}  & {82,11\%}                & {89,54\%}                & {75,9\%}                 & {71,78\%}            & {88,18\%}                & {76,72\%}                \\
        {3} & {50}  & {83,12\%}                & \textcolor{red}{90,82\%} & {77,62\%}                & {74,08\%}            & {88,88\%}                & {78,74\%}                \\
        {3} & {100} & {83,74\%}                & {89,59\%}                & {79,29\%}                & {74,48\%}            & \textbf{87,46\%}         & {78,05\%}                \\
        {4} & {2}   & {88,86\%}                & \textcolor{red}{94\%}    & {84,8\%}                 & {83,19\%}            & \textcolor{red}{93,37\%} & {85,92\%}                \\
        {4} & {10}  & \textbf{79,93\%}         & \textbf{89,29\%}         & \textbf{74,1\%}          & \textbf{69,5\%}      & \textbf{87,19\%}         & \textbf{74,79\%}         \\
        {4} & {16}  & \textbf{81,26\%}         & {89,68\%}                & \textbf{75,73\%}         & {71,96\%}            & {88,4\%}                 & {76,93\%}                \\
        {4} & {50}  & {81,55\%}                & {89,42\%}                & {75,9\%}                 & {71,68\%}            & {88,17\%}                & {76,55\%}                \\
        {6} & {2}   & \textcolor{red}{91,09\%} & \textcolor{red}{95,26\%} & {87,86\%}                & {86,81\%}            & \textcolor{red}{94,78\%} & {88,82\%}                \\
        {6} & {50}  & \textbf{80,39\%}         & \textbf{87,85\%}         & \textbf{75,01\%}         & \textbf{68,71\%}     & \textbf{84,54\%}         & \textbf{72,93\%}         \\
        \bottomrule
    \end{tabular}
    \caption{RE generator: Dale-5}
    \label{tab:probing:re-generator:dale-5}
\end{table}

@@

    \label{tab:probing:attribute-generator:dale-2}

@@

    \label{tab:probing:attribute-generator:dale-5}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si} & \textbf{Sh > Si > C} & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C} \\\midrule
        {1} & {2}   & \textcolor{red}{99,92\%} & \textcolor{red}{99,88\%} & \textbf{79,83\%}     & \textbf{82,7\%}      & \textcolor{red}{99,71\%} & \textbf{82,14\%}     \\
        {1} & {10}  & \textbf{70,52\%}         & \textbf{70,36\%}         & \textbf{80,23\%}     & \textbf{82,36\%}     & \textbf{74,49\%}         & \textbf{81,77\%}     \\
        {1} & {16}  & \textbf{77,25\%}         & \textbf{77,16\%}         & {84,55\%}            & {86,2\%}             & \textbf{80,72\%}         & {85,56\%}            \\
        {3} & {10}  & \textbf{71,46\%}         & \textbf{71,47\%}         & \textbf{78,81\%}     & \textbf{81,87\%}     & \textbf{75,95\%}         & \textbf{80,93\%}     \\
        {6} & {2}   & {83,25\%}                & {83,23\%}                & {87,74\%}            & {88,95\%}            & {85,38\%}                & {88,87\%}            \\
        \bottomrule
    \end{tabular}
    \caption{Attribute generator: Color}
    \label{tab:probing:attribute-generator:colour}
\end{table}

@@

    \label{tab:probing:attention-predictor:dale-2}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}              & \textbf{C > Si > Sh} & \textbf{Sh > C > Si}              & \textbf{Sh > Si > C} & \textbf{Si > C > Sh} & \textbf{Si > Sh > C} \\\midrule
        {1} & {2}   & \textcolor{red}{95,35\%}          & {89,87\%}            & \textcolor{red}{95,09\%}          & {87,23\%}            & {86,01\%}            & {84,14\%}            \\
        {1} & {16}  & \textcolor{red}{92,95\%}          & {87,03\%}            & \textcolor{red}{92,63\%}          & {83,91\%}            & {82,77\%}            & {80,06\%}            \\
        {1} & {50}  & \textcolor{red}{93,35\%}          & {87,23\%}            & \textcolor{red}{93,26\%}          & {84,65\%}            & {82,46\%}            & {80,38\%}            \\
        {2} & {10}  & \textbf{88,94\%}                  & \textbf{84,78\%}     & \textbf{87,5\%}                   & \textbf{77,76\%}     & \textbf{80,24\%}     & \textbf{74,95\%}     \\
        {2} & {16}  & \textbf{85,71\%}                  & \textbf{84,53\%}     & \textbf{82,98\%}                  & \textbf{72,85\%}     & \textbf{79,72\%}     & \textbf{71,85\%}     \\
        {3} & {16}  & \textcolor{red}{\textbf{92,18\%}} & \textbf{86,23\%}     & \textcolor{red}{91,93\%}          & \textbf{82,59\%}     & \textbf{81,69\%}     & \textbf{78,72\%}     \\
        {3} & {50}  & \textcolor{red}{92,68\%}          & {86,53\%}            & \textcolor{red}{91,9\%}           & {83,35\%}            & {82,45\%}            & {79,99\%}            \\
        {6} & {10}  & \textcolor{red}{93,4\%}           & {86,51\%}            & \textcolor{red}{\textbf{91,64\%}} & {84,03\%}            & {82,51\%}            & {80,06\%}            \\
        \bottomrule
    \end{tabular}
    \caption{Attention predictor: Dale-5}
    \label{tab:probing:attention-predictor:dale-5}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{cc|c|c|c|c|c|c}
        \toprule
        $n$ & $|V|$ & \textbf{C > Sh > Si}     & \textbf{C > Si > Sh}     & \textbf{Sh > C > Si}     & \textbf{Sh > Si > C}     & \textbf{Si > C > Sh}     & \textbf{Si > Sh > C}     \\\midrule
        {3} & {16}  & \textcolor{red}{98,48\%} & \textcolor{red}{98,58\%} & \textcolor{red}{97,87\%} & \textcolor{red}{96,11\%} & \textcolor{red}{96,6\%}  & \textcolor{red}{95,97\%} \\
        {4} & {10}  & \textcolor{red}{98,88\%} & \textcolor{red}{98,75\%} & \textcolor{red}{97,23\%} & \textcolor{red}{96,67\%} & \textcolor{red}{97,18\%} & \textcolor{red}{96,75\%} \\
        \bottomrule
    \end{tabular}
    \caption{Attention predictor: Color}
    \label{tab:probing:attention-predictor:colour}
\end{table}

An analysis of the frequency of used symbols and messages, as well as an examination for which images and objects they are used indicates the structure of the language and meanings of the symbols.
In a second step, the language is compared to several referring expressions in natural language.
By doing this, it can be seen if the models learned to use similar ways of referring to objects as humans do, or if they rely on different approaches.
% from prev chapter
